Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-07-10 manuscript/manuscript.Rmd
Updating significance statement w Anitra edits

>>>>

# Importance

Mesoscale eddies are common ocean surface currents that circulate seawater vertically and horizontally. This stirring effect alters biogeochemistry and planktonic community composition. Here, we use metabolomics to determine how these eddy-induced changes influence the nature of organic carbon across an eddy dipole. We found that many small, polar molecules track with the overall particulate carbon in the system and that there were significant differences in metabolite composition between eddy states. A few metabolites reflected the increased importance of eukaryotic phytoplankton that were enriched by the higher nutrient supply from depth in the cyclonic eddies. Anticyclones contained more compounds that reflected a higher degree of degradation. This work answers outstanding questions about the importance of these common ocean features in shaping microbial community function.
